A publishing infrastructure for AI-assisted academic authoring

### 2024-03-26 latex/manuscript.tex
introduction: shorten text

The tradition of scholarly writing dates back thousands of years, evolving significantly with the advent of scientific journals approximately 350 years ago {[}\protect\hyperlink{ref-F3iZfGUC}{1}{]}.
External peer review, used by many journals, is even more recent, having been around for less than 100 years {[}\protect\hyperlink{ref-1HMhNrQq1}{2}{]}.
Most manuscripts are written by individuals or teams working together to describe new advances, summarize existing literature, or argue for changes in the status quo.
However, scholarly writing is a time-consuming process in which the results of a study are presented using a specific style and format.
Academics can sometimes be long-winded in getting to key points, making their writing more impenetrable to their audience {[}\protect\hyperlink{ref-19YWsShi0}{3}{]}.

Recent advances in computing capabilities and the widespread availability of text, images, and other data on the internet have laid the foundation for artificial intelligence (AI) models with billions of parameters.
Large language models (LLMs), in particular, are opening the floodgates to new technologies with the capability to transform how society operates {[}\protect\hyperlink{ref-xq1uEbPa}{4}{]}.
OpenAI's models, for instance, have been trained on vast amounts of data and can generate human-like text {[}\protect\hyperlink{ref-bYOaJHMe}{5}{]}.
These models are based on the transformer architecture, which uses self-attention mechanisms to model the complexities of language.
The most well-known of these models is the Generative Pre-trained Transformer (GPT-3, and more recently, GPT-4), which is highly effective for a range of language tasks such as generating text, completing code, and answering questions {[}\protect\hyperlink{ref-bYOaJHMe}{5}{]}.
In the realm of medical informatics, scientists are beginning to explore the utility of these tools in optimizing clinical decision support {[}\protect\hyperlink{ref-gRhoGuC4}{6}{]} or assessing its potential to reduce health disparities {[}\protect\hyperlink{ref-CYB5vhZp}{7}{]}, while also raising concerns about their impact on medical education {[}\protect\hyperlink{ref-h8wInPLE}{8}{]} and the importance of keeping the human aspect central in AI development and application {[}\protect\hyperlink{ref-Z2ek25Ak}{9}{]}.
These tools have also been used to enhance scientific communication {[}\protect\hyperlink{ref-Svww2RUh}{10}{]}.
This technology has the potential to revolutionize how scientists write and revise scholarly manuscripts, saving time and effort and enabling researchers to focus on more high-level tasks such as data analysis and interpretation.
However, using LLMs in research has sparked controversy, primarily due to their propensity to generate plausible yet factually incorrect or misleading information.

In this work, we present a human-centric approach for using AI in manuscript writing, where scholarly text, initially created by humans, is revised through edit suggestions from LLMs and is ultimately reviewed and approved by humans.
This approach mitigates the risk of generating misleading information while still providing the benefits of AI-assisted writing.
We developed an AI-assisted revision tool that implements this approach and builds on the Manubot infrastructure for scholarly publishing {[}\protect\hyperlink{ref-YuJbg3zO}{11}{]}, a platform designed to enable both individual and large-scale collaborative projects {[}\protect\hyperlink{ref-PZMP42Ak}{12},\protect\hyperlink{ref-10gsAq0o}{13}{]}.
Our tool, named the Manubot AI Editor, parses the manuscript, utilizes an LLM with section-specific prompts for revision, and then generates a set of suggested changes to be integrated into the main document.
These changes are presented to the user through the GitHub interface for review.
During prompt engineering, we developed unit tests to ensure that the AI revisions met a minimum set of quality measures.
For an end-to-end evaluation, we applied our tool to five manuscripts that included sections of varying complexity.
We performed 1) a human evaluation by manually reviewing the AI revisions, and 2) an automatic evaluation using the LLM-as-a-Judge technique {[}\protect\hyperlink{ref-LhEwBH2w}{14}{]} to assess the quality of the AI revisions.
Our findings indicate that, in most cases, the models could maintain the original meaning of the text, improve the writing style, and even interpret mathematical expressions.
Officially part of the Manubot platform, our Manubot AI Editor can be readily incorporated into Manubot-based manuscripts, and we anticipate it will help authors more effectively communicate their work.

@@

We propose a human-centric approach for the use of AI in manuscript writing, which consists of the following steps:
1) human authors write the manuscript content;
2) an LLM revises the manuscript, generating a set of suggested changes;
3) human authors review the suggested changes, and the approved edits are then integrated into the manuscript.
By focusing on human review, this approach attempts to mitigate the risk of generating incorrect or misleading information.
To implement this human-centric approach, we developed a tool called the Manubot AI Editor, which is part of the Manubot infrastructure for scholarly publishing {[}\protect\hyperlink{ref-YuJbg3zO}{11}{]}.

@@

The Manubot AI Editor is an AI-based revision infrastructure integrated into Manubot {[}\protect\hyperlink{ref-YuJbg3zO}{11}{]}, a tool for collaborative writing of scientific manuscripts.
Manubot integrates with popular version control platforms such as GitHub, allowing authors to easily track changes and collaborate on writing in real time.
Furthermore, Manubot automates the process of generating a formatted manuscript (e.g., HTML, PDF, DOCX; Figure \ref{fig:ai_revision}a shows the HTML output).
Built upon this modern and open paradigm, our Manubot AI Editor (\url{https://github.com/manubot/manubot-ai-editor}) includes three components:
1) a Python library that provides classes and functions to read the manuscript content and its metadata, calls the LLM for automatic text revision, and writes the results back;
2) a GitHub Actions workflow that uses our Python library within GitHub to preserve provenance information for transparency;
3) a prompt generator that integrates the manuscript's metadata using prompt templates to generate section-specific prompts for each paragraph (Figure \ref{fig:ai_revision}b).

@@

For the evaluation of our tool, we conducted manual assessments performed by humans and automatic assessments performed by an LLM.
For the human assessments, we used three of our own manuscripts (Table \ref{tbl:manuscripts}): the Clustermatch Correlation Coefficient (CCC) {[}\protect\hyperlink{ref-eirYTTyk}{15}{]}, PhenoPLIER {[}\protect\hyperlink{ref-NM3rHx1i}{16}{]}, and Manubot-AI (this manuscript).
CCC is a new correlation coefficient applied to transcriptomic data, while PhenoPLIER is a framework consisting of three different methods used in genetic studies.
CCC falls under the field of computational biology, whereas PhenoPLIER pertains to genomic medicine.
CCC outlines one computational method applied to a specific data type (correlation to gene expression).
In contrast, PhenoPLIER describes a framework that integrates three different approaches (regression, clustering, and drug-disease prediction) using data from genome-wide and transcription-wide association studies (GWAS and TWAS), gene expression, and transcriptional responses to small molecule perturbations.
Thus, CCC has a simpler structure, while PhenoPLIER is a more complex manuscript with additional figures and tables, along with a Methods section that includes equations.
The third manuscript, Manubot-AI, has a much simpler structure and was written and revised using our tool prior to submission, demonstrating a practical AI-based revision use case.
For the automatic assessments, we incorporated two external manuscripts (with IDs BioChatter and Epistasis in Table \ref{tbl:manuscripts}).

@@

For this evaluation, we ran our workflow on manuscripts CCC, PhenoPLIER, BioChatter, and Epistasis using the GPT-3.5 Turbo model (\texttt{gpt-3.5-turbo}).
We then inspected each PR and manually matched all pairs of original and revised paragraphs, across the abstract, introduction, methods, results, and supplementary material sections.
This procedure generated 31 paragraph pairs for CCC, 63 for PhenoPLIER, 37 for BioChatter, and 63 for Epistasis.
Using the LLM-as-a-Judge method {[}\protect\hyperlink{ref-LhEwBH2w}{14}{]}, we evaluated the quality of the revisions using both GPT-3.5 Turbo (\texttt{gpt-3.5-turbo}) and GPT-4 Turbo (\texttt{gpt-4-turbo-preview}) as judges.
The judge is asked to decide which of the two paragraphs in each pair is better or if they are equally good (tie).
For this, we used prompt chaining, where the judge first evaluates the quality of each paragraph independently by writing a list with positive and negative aspects in the following areas: 1) clear sentence structure, 2) ease of understanding, 3) grammatical correctness, 4) absence of spelling errors.
Then, the judge was asked to be as objective as possible and decide if one of the paragraphs is clearly better than the other or if they are similar in quality, while also providing a rationale for the decision.
We also accounted for the case of position bias {[}\protect\hyperlink{ref-LhEwBH2w}{14}{]} (i.e., the order in which the paragraphs were presented could influence the decision) by swapping the order of the paragraphs.
Each assessment was repeated ten times.
The full prompt chain can be seen in Supplementary File 4, which includes an example of the output in each step generated by GPT-4 Turbo as a judge.

@@

We tested the tool on a paragraph from the Results section of CCC (Figure \ref{fig:results:ccc}).
This paragraph describes Figure 1 of the CCC manuscript {[}\protect\hyperlink{ref-eirYTTyk}{15}{]}, which showcases four different datasets, each with two variables, and various relationships or patterns labeled as random/independent, non-coexistence, quadratic, and two-lines.
The revised paragraph, while having fewer sentences, is slightly longer and consistently uses the past tense, unlike the original one which has tense shifts.
The revised paragraph also retains all citations, which, although not explicitly mentioned in the prompts for this section (as it is for introductions), is important in this case.
The original LaTeX format was maintained for the math, and the figure was correctly referenced using the Manubot syntax.
In the third sentence of the revised paragraph (line 3), the model generated a good summary of how all coefficients performed in the last two nonlinear patterns, and why CCC was able to capture them.
As human authors, we would make a single change at the end of this sentence to avoid repeating the word ``complexity'': \emph{``\ldots, while CCC increased the model's complexity \sout{by using different degrees of complexity} to capture the relationships.''}
The revised paragraph is more concise and clearly describes what the figure shows and how CCC works.
It's remarkable that the model rewrote some of the concepts in the original paragraph (lines 4 to 8) into three new sentences (lines 3 to 5) with the same meaning, but more concisely and clearly.
The model also produced high-quality revisions for several other paragraphs that would only need minor changes.

@@

We designed section-specific prompts to guide the revision of text using GPT-3.
Surprisingly, in one Methods section, the model detected an error when referencing a symbol in an equation that had been overlooked by humans.
However, revising abstracts proved more challenging for the model, as revisions often removed background information about the research problem.
There are opportunities to improve the AI-based revisions, such as further refining prompts using few-shot learning {[}\protect\hyperlink{ref-S1Lim9f9}{17}{]}, or fine-tuning the model using an additional corpus of academic writing focused on particularly challenging sections.
Fine-tuning using preprint-publication pairs {[}\protect\hyperlink{ref-WVt383GU}{18}{]} may help to identify sections or phrases likely to be changed during peer review.
Our approach processed each paragraph of the text but lacked a contextual thread between queries, which mainly affected the Results and Methods sections.
Using chatbots that retain context could enable the revision of individual paragraphs while considering previously processed text.
We plan to update our workflow to support this strategy.
Open and semi-open models, such as BLOOM {[}\protect\hyperlink{ref-I4d1F0yv}{19}{]}, Meta's Llama 2 {[}\protect\hyperlink{ref-A213xAuD}{20}{]}, and Mistral 7B {[}\protect\hyperlink{ref-1wOalSCp}{21}{]}, are growing in popularity and capabilities, but they lack the user-friendly OpenAI API.
Despite these limitations, we found that models captured the main ideas and generated a revision that often communicated the intended meaning more clearly and concisely.
While our study focused on OpenAI's GPT-3 and GPT-3.5 Turbo for revisions, the Manubot AI Editor is prepared to support future models.

@@

The use of AI-assisted tools for scientific authoring is controversial {[}\protect\hyperlink{ref-1EAonKBXJ}{22},\protect\hyperlink{ref-KJTJqmxc}{23}{]}.
Questions arise concerning the originality and ownership of texts generated by these models.
For example, the \emph{Nature} journal has established that any use of these models in scientific writing must be documented {[}\protect\hyperlink{ref-wQLVc4o7}{24}{]}, and the International Conference on Machine Learning (ICML) has prohibited the submission of \emph{``papers that include text generated from a large-scale language model (LLM)''} {[}\protect\hyperlink{ref-K58CKD6D}{25}{]}, although editing tools for grammar and spelling correction are allowed.
Our work, however, focuses on revising \emph{existing} text written by a human author.
Additionally, all changes made by humans and AI are tracked in the version control system, which allows for full transparency.
Despite the concerns, there are also significant opportunities.
Our work lays the foundation for a future in which humans and machines construct academic manuscripts together.
Scientific articles need to adhere to a certain style, which can make the writing time-consuming and require a significant amount of effort to think about \emph{how} to communicate a result or finding that has already been obtained.
As machines become increasingly capable of improving scholarly text, humans can focus more on \emph{what} to communicate to others, rather than on \emph{how} to write it.
This could lead to a more equitable and productive future for research, where scientists are only limited by their ideas and ability to conduct experiments to uncover the underlying organizing principles of ourselves and our environment.

@@

\leavevmode\vadjust pre{\hypertarget{ref-xq1uEbPa}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{\textbf{Understanding the Capabilities, Limitations, and Societal Impact of Large Language Models}
\CSLBlock{Alex Tamkin, Miles Brundage, Jack Clark, Deep Ganguli} \emph{arXiv} (2021-02-05) \url{https://arxiv.org/abs/2102.02503}}

\leavevmode\vadjust pre{\hypertarget{ref-bYOaJHMe}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{\textbf{Language Models are Few-Shot Learners}
\CSLBlock{Tom B Brown, Benjamin Mann, Nick Ryder, Melanie Subbiah, Jared Kaplan, Prafulla Dhariwal, Arvind Neelakantan, Pranav Shyam, Girish Sastry, Amanda Askell, \ldots{} Dario Amodei} \emph{arXiv} (2020-07-24) \url{https://arxiv.org/abs/2005.14165}}

\leavevmode\vadjust pre{\hypertarget{ref-gRhoGuC4}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{\textbf{Using AI-generated suggestions from ChatGPT to optimize clinical decision support}
\CSLBlock{Siru Liu, Aileen P Wright, Barron L Patterson, Jonathan P Wanderer, Robert W Turer, Scott D Nelson, Allison B McCoy, Dean F Sittig, Adam Wright} \emph{Journal of the American Medical Informatics Association} (2023-04-22) \url{https://doi.org/gsgvw2}
\CSLBlock{DOI: \href{https://doi.org/10.1093/jamia/ocad072}{10.1093/jamia/ocad072} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/37087108}{37087108} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10280357}{PMC10280357}}}

\leavevmode\vadjust pre{\hypertarget{ref-CYB5vhZp}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{\textbf{Benchmarking the symptom-checking capabilities of ChatGPT for a broad range of diseases}
\CSLBlock{Anjun Chen, Drake O Chen, Lu Tian} \emph{Journal of the American Medical Informatics Association} (2023-12-18) \url{https://doi.org/10.1093/jamia/ocad245}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Svww2RUh}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{\textbf{Could AI help you to write your next paper?}
\CSLBlock{Matthew Hutson} \emph{Nature} (2022-10-31) \url{https://doi.org/grpm4w}
\CSLBlock{DOI: \href{https://doi.org/10.1038/d41586-022-03479-w}{10.1038/d41586-022-03479-w} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/36316468}{36316468}}}

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{\textbf{Open collaborative writing with Manubot}
\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}

\leavevmode\vadjust pre{\hypertarget{ref-PZMP42Ak}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{\textbf{Opportunities and obstacles for deep learning in biology and medicine}
\CSLBlock{Travers Ching, Daniel S Himmelstein, Brett K Beaulieu-Jones, Alexandr A Kalinin, Brian T Do, Gregory P Way, Enrico Ferrero, Paul-Michael Agapow, Michael Zietz, Michael M Hoffman, \ldots{} Casey S Greene} \emph{Journal of The Royal Society Interface} (2018-04) \url{https://doi.org/gddkhn}
\CSLBlock{DOI: \href{https://doi.org/10.1098/rsif.2017.0387}{10.1098/rsif.2017.0387} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29618526}{29618526} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5938574}{PMC5938574}}}

\leavevmode\vadjust pre{\hypertarget{ref-10gsAq0o}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{\textbf{An Open-Publishing Response to the COVID-19 Infodemic.}
\CSLBlock{Halie M Rando, Simina M Boca, Lucy D\textquotesingle Agostino McGowan, Daniel S Himmelstein, Michael P Robson, Vincent Rubinetti, Ryan Velazquez, Casey S Greene, Anthony Gitter} \emph{ArXiv} (2021-09-17) \url{https://www.ncbi.nlm.nih.gov/pubmed/34545336}
\CSLBlock{PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/34545336}{34545336} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8452106}{PMC8452106}}}

\leavevmode\vadjust pre{\hypertarget{ref-LhEwBH2w}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{\textbf{Judging LLM-as-a-Judge with MT-Bench and Chatbot Arena}
\CSLBlock{Lianmin Zheng, Wei-Lin Chiang, Ying Sheng, Siyuan Zhuang, Zhanghao Wu, Yonghao Zhuang, Zi Lin, Zhuohan Li, Dacheng Li, EricP Xing, \ldots{} Ion Stoica} \emph{arXiv} (2023-10-17) \url{https://arxiv.org/abs/2306.05685}}

>>>>

Scholarly writing has evolved since the first scientific journals 350 years ago, adopting practices like external peer review in the last century {[}\protect\hyperlink{ref-F3iZfGUC}{1},\protect\hyperlink{ref-1HMhNrQq1}{2}{]}.
It often involves dense language to convey new advances or literature summaries {[}\protect\hyperlink{ref-19YWsShi0}{3}{]}.
Meanwhile, recent computing advances have enabled large language models (LLMs) like OpenAI's GPT-3 and GPT-4 {[}\protect\hyperlink{ref-bYOaJHMe}{4}{]}, revolutionizing technologies and applications in various fields, including medical informatics and scientific communication {[}\protect\hyperlink{ref-gRhoGuC4}{5},\protect\hyperlink{ref-CYB5vhZp}{6}{]}.
These models promise to streamline scientific writing {[}\protect\hyperlink{ref-Svww2RUh}{7}{]}, though their use raises accuracy and ethical concerns {[}\protect\hyperlink{ref-h8wInPLE}{8},\protect\hyperlink{ref-Z2ek25Ak}{9}{]}.

We introduce a human-centric AI method for scholarly writing, leveraging LLMs for draft revision within the Manubot platform, a tool for collaborative publishing {[}\protect\hyperlink{ref-YuJbg3zO}{10}{]}.
Here, we propose the Manubot AI Editor, which suggests revisions via GitHub, balancing AI's efficiency with human oversight to ensure accuracy.
Tested on five manuscripts, we found it maintained the original meaning, improved style, and handled complex expressions, proving a valuable addition to the Manubot suite.
We anticipate our tool will help authors more effectively communicate their work.

@@

We propose a human-centric approach for the use of AI in manuscript writing, which consists of the following steps:
1) human authors write the manuscript content;
2) an LLM revises the manuscript, generating a set of suggested changes;
3) human authors review the suggested changes, and the approved edits are then integrated into the manuscript.
By focusing on human review, this approach attempts to mitigate the risk of generating incorrect or misleading information.
To implement this human-centric approach, we developed a tool called the Manubot AI Editor, which is part of the Manubot infrastructure for scholarly publishing {[}\protect\hyperlink{ref-YuJbg3zO}{10}{]}.

@@

The Manubot AI Editor is an AI-based revision infrastructure integrated into Manubot {[}\protect\hyperlink{ref-YuJbg3zO}{10}{]}, a tool for collaborative writing of scientific manuscripts.
Manubot integrates with popular version control platforms such as GitHub, allowing authors to easily track changes and collaborate on writing in real time.
Furthermore, Manubot automates the process of generating a formatted manuscript (e.g., HTML, PDF, DOCX; Figure \ref{fig:ai_revision}a shows the HTML output).
Built upon this modern and open paradigm, our Manubot AI Editor (\url{https://github.com/manubot/manubot-ai-editor}) includes three components:
1) a Python library that provides classes and functions to read the manuscript content and its metadata, calls the LLM for automatic text revision, and writes the results back;
2) a GitHub Actions workflow that uses our Python library within GitHub to preserve provenance information for transparency;
3) a prompt generator that integrates the manuscript's metadata using prompt templates to generate section-specific prompts for each paragraph (Figure \ref{fig:ai_revision}b).

@@

For the evaluation of our tool, we conducted manual assessments performed by humans and automatic assessments performed by an LLM.
For the human assessments, we used three of our own manuscripts (Table \ref{tbl:manuscripts}): the Clustermatch Correlation Coefficient (CCC) {[}\protect\hyperlink{ref-eirYTTyk}{11}{]}, PhenoPLIER {[}\protect\hyperlink{ref-NM3rHx1i}{12}{]}, and Manubot-AI (this manuscript).
CCC is a new correlation coefficient applied to transcriptomic data, while PhenoPLIER is a framework consisting of three different methods used in genetic studies.
CCC falls under the field of computational biology, whereas PhenoPLIER pertains to genomic medicine.
CCC outlines one computational method applied to a specific data type (correlation to gene expression).
In contrast, PhenoPLIER describes a framework that integrates three different approaches (regression, clustering, and drug-disease prediction) using data from genome-wide and transcription-wide association studies (GWAS and TWAS), gene expression, and transcriptional responses to small molecule perturbations.
Thus, CCC has a simpler structure, while PhenoPLIER is a more complex manuscript with additional figures and tables, along with a Methods section that includes equations.
The third manuscript, Manubot-AI, has a much simpler structure and was written and revised using our tool prior to submission, demonstrating a practical AI-based revision use case.
For the automatic assessments, we incorporated two external manuscripts (with IDs BioChatter and Epistasis in Table \ref{tbl:manuscripts}).

@@

For this evaluation, we ran our workflow on manuscripts CCC, PhenoPLIER, BioChatter, and Epistasis using the GPT-3.5 Turbo model (\texttt{gpt-3.5-turbo}).
We then inspected each PR and manually matched all pairs of original and revised paragraphs, across the abstract, introduction, methods, results, and supplementary material sections.
This procedure generated 31 paragraph pairs for CCC, 63 for PhenoPLIER, 37 for BioChatter, and 63 for Epistasis.
Using the LLM-as-a-Judge method {[}\protect\hyperlink{ref-LhEwBH2w}{13}{]}, we evaluated the quality of the revisions using both GPT-3.5 Turbo (\texttt{gpt-3.5-turbo}) and GPT-4 Turbo (\texttt{gpt-4-turbo-preview}) as judges.
The judge is asked to decide which of the two paragraphs in each pair is better or if they are equally good (tie).
For this, we used prompt chaining, where the judge first evaluates the quality of each paragraph independently by writing a list with positive and negative aspects in the following areas: 1) clear sentence structure, 2) ease of understanding, 3) grammatical correctness, 4) absence of spelling errors.
Then, the judge was asked to be as objective as possible and decide if one of the paragraphs is clearly better than the other or if they are similar in quality, while also providing a rationale for the decision.
We also accounted for the case of position bias {[}\protect\hyperlink{ref-LhEwBH2w}{13}{]} (i.e., the order in which the paragraphs were presented could influence the decision) by swapping the order of the paragraphs.
Each assessment was repeated ten times.
The full prompt chain can be seen in Supplementary File 4, which includes an example of the output in each step generated by GPT-4 Turbo as a judge.

@@

We tested the tool on a paragraph from the Results section of CCC (Figure \ref{fig:results:ccc}).
This paragraph describes Figure 1 of the CCC manuscript {[}\protect\hyperlink{ref-eirYTTyk}{11}{]}, which showcases four different datasets, each with two variables, and various relationships or patterns labeled as random/independent, non-coexistence, quadratic, and two-lines.
The revised paragraph, while having fewer sentences, is slightly longer and consistently uses the past tense, unlike the original one which has tense shifts.
The revised paragraph also retains all citations, which, although not explicitly mentioned in the prompts for this section (as it is for introductions), is important in this case.
The original LaTeX format was maintained for the math, and the figure was correctly referenced using the Manubot syntax.
In the third sentence of the revised paragraph (line 3), the model generated a good summary of how all coefficients performed in the last two nonlinear patterns, and why CCC was able to capture them.
As human authors, we would make a single change at the end of this sentence to avoid repeating the word ``complexity'': \emph{``\ldots, while CCC increased the model's complexity \sout{by using different degrees of complexity} to capture the relationships.''}
The revised paragraph is more concise and clearly describes what the figure shows and how CCC works.
It's remarkable that the model rewrote some of the concepts in the original paragraph (lines 4 to 8) into three new sentences (lines 3 to 5) with the same meaning, but more concisely and clearly.
The model also produced high-quality revisions for several other paragraphs that would only need minor changes.

@@

We designed section-specific prompts to guide the revision of text using GPT-3.
Surprisingly, in one Methods section, the model detected an error when referencing a symbol in an equation that had been overlooked by humans.
However, revising abstracts proved more challenging for the model, as revisions often removed background information about the research problem.
There are opportunities to improve the AI-based revisions, such as further refining prompts using few-shot learning {[}\protect\hyperlink{ref-S1Lim9f9}{14}{]}, or fine-tuning the model using an additional corpus of academic writing focused on particularly challenging sections.
Fine-tuning using preprint-publication pairs {[}\protect\hyperlink{ref-WVt383GU}{15}{]} may help to identify sections or phrases likely to be changed during peer review.
Our approach processed each paragraph of the text but lacked a contextual thread between queries, which mainly affected the Results and Methods sections.
Using chatbots that retain context could enable the revision of individual paragraphs while considering previously processed text.
We plan to update our workflow to support this strategy.
Open and semi-open models, such as BLOOM {[}\protect\hyperlink{ref-I4d1F0yv}{16}{]}, Meta's Llama 2 {[}\protect\hyperlink{ref-A213xAuD}{17}{]}, and Mistral 7B {[}\protect\hyperlink{ref-1wOalSCp}{18}{]}, are growing in popularity and capabilities, but they lack the user-friendly OpenAI API.
Despite these limitations, we found that models captured the main ideas and generated a revision that often communicated the intended meaning more clearly and concisely.
While our study focused on OpenAI's GPT-3 and GPT-3.5 Turbo for revisions, the Manubot AI Editor is prepared to support future models.

@@

The use of AI-assisted tools for scientific authoring is controversial {[}\protect\hyperlink{ref-1EAonKBXJ}{19},\protect\hyperlink{ref-KJTJqmxc}{20}{]}.
Questions arise concerning the originality and ownership of texts generated by these models.
For example, the \emph{Nature} journal has established that any use of these models in scientific writing must be documented {[}\protect\hyperlink{ref-wQLVc4o7}{21}{]}, and the International Conference on Machine Learning (ICML) has prohibited the submission of \emph{``papers that include text generated from a large-scale language model (LLM)''} {[}\protect\hyperlink{ref-K58CKD6D}{22}{]}, although editing tools for grammar and spelling correction are allowed.
Our work, however, focuses on revising \emph{existing} text written by a human author.
Additionally, all changes made by humans and AI are tracked in the version control system, which allows for full transparency.
Despite the concerns, there are also significant opportunities.
Our work lays the foundation for a future in which humans and machines construct academic manuscripts together.
Scientific articles need to adhere to a certain style, which can make the writing time-consuming and require a significant amount of effort to think about \emph{how} to communicate a result or finding that has already been obtained.
As machines become increasingly capable of improving scholarly text, humans can focus more on \emph{what} to communicate to others, rather than on \emph{how} to write it.
This could lead to a more equitable and productive future for research, where scientists are only limited by their ideas and ability to conduct experiments to uncover the underlying organizing principles of ourselves and our environment.

@@

\leavevmode\vadjust pre{\hypertarget{ref-bYOaJHMe}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{\textbf{Language Models are Few-Shot Learners}
\CSLBlock{Tom B Brown, Benjamin Mann, Nick Ryder, Melanie Subbiah, Jared Kaplan, Prafulla Dhariwal, Arvind Neelakantan, Pranav Shyam, Girish Sastry, Amanda Askell, \ldots{} Dario Amodei} \emph{arXiv} (2020-07-24) \url{https://arxiv.org/abs/2005.14165}}

\leavevmode\vadjust pre{\hypertarget{ref-gRhoGuC4}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{\textbf{Using AI-generated suggestions from ChatGPT to optimize clinical decision support}
\CSLBlock{Siru Liu, Aileen P Wright, Barron L Patterson, Jonathan P Wanderer, Robert W Turer, Scott D Nelson, Allison B McCoy, Dean F Sittig, Adam Wright} \emph{Journal of the American Medical Informatics Association} (2023-04-22) \url{https://doi.org/gsgvw2}
\CSLBlock{DOI: \href{https://doi.org/10.1093/jamia/ocad072}{10.1093/jamia/ocad072} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/37087108}{37087108} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10280357}{PMC10280357}}}

\leavevmode\vadjust pre{\hypertarget{ref-CYB5vhZp}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{\textbf{Benchmarking the symptom-checking capabilities of ChatGPT for a broad range of diseases}
\CSLBlock{Anjun Chen, Drake O Chen, Lu Tian} \emph{Journal of the American Medical Informatics Association} (2023-12-18) \url{https://doi.org/10.1093/jamia/ocad245}}

\leavevmode\vadjust pre{\hypertarget{ref-Svww2RUh}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{\textbf{Could AI help you to write your next paper?}
\CSLBlock{Matthew Hutson} \emph{Nature} (2022-10-31) \url{https://doi.org/grpm4w}
\CSLBlock{DOI: \href{https://doi.org/10.1038/d41586-022-03479-w}{10.1038/d41586-022-03479-w} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/36316468}{36316468}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{\textbf{Open collaborative writing with Manubot}
\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}

\leavevmode\vadjust pre{\hypertarget{ref-eirYTTyk}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{\textbf{An efficient not-only-linear correlation coefficient based on machine learning}
\CSLBlock{Milton Pividori, Marylyn D Ritchie, Diego H Milone, Casey S Greene} \emph{Cold Spring Harbor Laboratory} (2022-06-17) \url{https://doi.org/gqcvbw}
\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.06.15.496326}{10.1101/2022.06.15.496326}}}

\leavevmode\vadjust pre{\hypertarget{ref-NM3rHx1i}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{\textbf{Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms}
\CSLBlock{Milton Pividori, Sumei Lu, Binglan Li, Chun Su, Matthew E Johnson, Wei-Qi Wei, Qiping Feng, Bahram Namjou, Krzysztof Kiryluk, Iftikhar J Kullo, \ldots{} } \emph{Nature Communications} (2023-09-09) \url{https://doi.org/gspsxr}
\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-023-41057-4}{10.1038/s41467-023-41057-4} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/37689782}{37689782} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10492839}{PMC10492839}}}

\leavevmode\vadjust pre{\hypertarget{ref-LhEwBH2w}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{\textbf{Judging LLM-as-a-Judge with MT-Bench and Chatbot Arena}
\CSLBlock{Lianmin Zheng, Wei-Lin Chiang, Ying Sheng, Siyuan Zhuang, Zhanghao Wu, Yonghao Zhuang, Zi Lin, Zhuohan Li, Dacheng Li, EricP Xing, \ldots{} Ion Stoica} \emph{arXiv} (2023-10-17) \url{https://arxiv.org/abs/2306.05685}}

\leavevmode\vadjust pre{\hypertarget{ref-S1Lim9f9}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{\textbf{Generalizing from a Few Examples}
\CSLBlock{Yaqing Wang, Quanming Yao, James T Kwok, Lionel M Ni} \emph{ACM Computing Surveys} (2020-06-12) \url{https://doi.org/gg37m2}
\CSLBlock{DOI: \href{https://doi.org/10.1145/3386252}{10.1145/3386252}}}

\leavevmode\vadjust pre{\hypertarget{ref-WVt383GU}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{\textbf{Examining linguistic shifts between preprints and publications}
\CSLBlock{David N Nicholson, Vincent Rubinetti, Dongbo Hu, Marvin Thielk, Lawrence E Hunter, Casey S Greene} \emph{PLOS Biology} (2022-02-01) \url{https://doi.org/gqqzn2}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pbio.3001470}{10.1371/journal.pbio.3001470} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35104289}{35104289} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8806061}{PMC8806061}}}
